Do larger watersheds respond different to forest cover change? Re-analysing a global data set.

### 2022-01-01 paper/Forest_and_Water/Forest_and_Water.Rmd
test new laptop

Here $X_i$ are factorial variables, while $Z_i$ are continous variables. The model assumes no direct interactions and all variables are additive. The changes in forest cover contain both positive (forestation) and negative values (deforestation). In @zhang2017, these changes were jointly analysed, assuming the effect on the change in flow was linear and non-hysteretic. However, the impact of an increase in forest cover can be different from the same fractional decrease in forest cover. Therefore all the change in forest cover data is converted to positive values, and an additional column (*sign_{forest cover}*) is added that indicates whether it was a forest cover increase or decrease. 
A further assumption in the model is that all continuous variables $Z_i$ (such as annual precipitation (Pa)) can have a linear or non-linear relationship with $\Delta Q \%$. This means that a smooth function $s()$ is applied to the $Z_i$ variables. For the smoothing function we applied thin plate regression splines with an additional shrinkage penalty which means the terms can be shrunk to 0 if not significant [@wood2006].

>>>>

Here $X_i$ are factorial variables, while $Z_i$ are continuous variables. The model assumes no direct interactions and all variables are additive. The changes in forest cover contain both positive (forestation) and negative values (deforestation). In @zhang2017, these changes were jointly analysed, assuming the effect on the change in flow was linear and the effect if removing forest cover was the same as an equivalent reforestation. However, the impact of an increase in forest cover can be different from the same fractional decrease in forest cover. Therefore all the change in forest cover data is converted to positive values, and an additional column (*sign_{forest cover}*) is added that indicates whether it was a forest cover increase or decrease. 
A further assumption in the model is that all continuous variables $Z_i$ (such as annual precipitation (Pa)) can have a linear or non-linear relationship with $\Delta Q \%$. This means that a smooth function $s()$ is applied to the $Z_i$ variables. For the smoothing function we applied thin plate regression splines with an additional shrinkage penalty which means the terms can be shrunk to 0 if not significant [@wood2006].
